Effects of the body force on the evacuation dynamics

### 2019-12-27 paper.tex
agregue las figuras de overlap vs densidad y degree vs densidad
Update paper.tex

@@

>>>>

The Social Force Model (SFM) provides the necessary framework for simulating 
the collective dynamics of self-driven particles (\textit{i.e.} pedestrians). 
The pedestrians are considered to follow an equation of motion involving 
either ``socio-psychological'' forces and physical forces (say, granular 
forces). The equation of motion for any pedestrian $i$ (of mass $m_i$) reads

\begin{equation}
 m_i\,\displaystyle\frac{d\mathbf{v}_i}{dt}=\mathbf{f}_d^{(i)}+
 \displaystyle\sum_{j=1}^N\mathbf{f}_s^{(ij)}+
 \displaystyle\sum_{j=1}^N\mathbf{f}_g^{(ij)}\label{eqn_motion}
\end{equation}

\noindent where the subscript $j$ corrresponds to any neighboring pedestrian or 
the walls. The three forces $\mathbf{f}_d$, $\mathbf{f}_s$ and $\mathbf{f}_g$ 
are different in nature. The desire force $\mathbf{f}_d$ represents the 
acceleration (or deceleration) of the pedestrian due to his (her) own willings. 
The social force $\mathbf{f}_s$, intead, describes the tendency of the 
pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
stands for either the sliding friction and the compression between 
pedestrians. \\

Notice that these forces are supposed to influence the behavior of the 
pedestrians in a similar fashion as mentioned in Section~\ref{experimental}. 
Thus, the set of (empirical) parameters described in Section~\ref{experimental} 
is expected to be also present in the SFM. These will appear in connection to 
the forces, although their meaning may be somewhat different. \\

The pedestrians' own willing is modeled by the desire force $\mathbf{f}_d$. 
This force stands for the acceleration (deceleration) required to reach a 
certain position at the desired walking speed $v_d$. This involves, however, a 
personal attitude that makes him (her) appear more or less ``assertive''. As 
mentioned in Section~\ref{experimental}, the reaction time $\tau$  attains for 
this attitude. Thus, the desire force is modeled as follows

\begin{equation}
\mathbf{f}_d^{(i)}=m\,\displaystyle\frac{v_d^{(i)}\,
\hat{\mathbf{e}}_d^{(i)}(t)-
 \mathbf{v}^{(i)}(t)}{\tau}
\end{equation}

\noindent where $\hat{\mathbf{e}}(t)$ represents the unit vector pointing to 
the target position. $\mathbf{v}(t)$ stands for the pedestrian velocity at time 
$t$. \\

The tendency of any individual to preserve his (her) ``private sphere'' is 
accomplished by the social force $\mathbf{f}_s$. This force is expected to 
prevent the pedestrians from getting too close to each other (or to the walls) 
in a crowded environment. If he (she) perceives that there is not enough space 
to move, he (she) will decelerate or even move back. The model for this kind of 
``socio-psychological'' behavior is as follows

\begin{equation}
 \mathbf{f}_s^{(i)}=A\,e^{(R_{ij}-r_{ij})/B}\hat{\mathbf{n}}_{ij}
 \label{eqn_social}
\end{equation}

\noindent where $r_{ij}$ means the distance between the center of mass of the 
pedestrians $i$ and $j$, and $R_{ij}=R_i+R_j$ is the sum of the pedestrians 
radius. The unit vector $\hat{\mathbf{n}}_{ij}$ points from pedestrian $j$ to 
pedestrian $i$, meaning a repulsive interaction.\\

The net distance $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
expression (\ref{eqn_social}). This parameter plays the role of a fall-off 
length within the model, and thus, it may be somewhat connected to the 
(perceived) step distance mentioned in Section~\ref{experimental}. The 
parameter $A$, however, does not provide any direct link to other parameters 
mentioned there. \\

The granular force (say, the sliding friction plus the body force) attain to 
the moving difficulties encountered in very crowded environments. The 
expression for the granular force is has been borrowed from other granular 
matter fields, as follows

\begin{equation}
 \mathbf{f}_g^{(ij)}=\kappa\,(R_{ij}-r_{ij})\,\Theta(R_{ij}-r_{ij})
\,(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
k\,(R_{ij}-r_{ij})\,\Theta(R_{ij}\,\hat{\mathbf{n}}_{ij}
-r_{ij})\label{eqn_friction}
\end{equation}

\noindent where $\Theta(R_{ij}-r_{ij})$ equals unity if $R_{ij}>r_{ij}$ and 
vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
represents the difference between the tangential velocities of the sliding 
bodies (or between the individual and the walls).    \\

The sliding friction occurs in the tangential direction while the body force 
occurs in the normal direction. Both are assumed to be linear with respect to 
the net distance between contacting pedestrians. The sliding friction is also 
linearly related to the difference between the (tangential) velocities. The 
coefficients $\kappa$ (for the sliding friction) and $k$ (for the 
body force) are supposed to be related to the areas of contact and the clothes 
material, among others. \\

We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
$\kappa$ and $k$. This may not be completely true according to 
Table~\ref{table_data}. The local density (and thus, the pedestrians' 
compression) may affect the compressibility parameter $k$ by more than an order 
of magnitude. We will vary $k$ (and $\kappa$) in order to explore this 
phenomenon. \\

\subsection{\label{sfm}The parameters setting}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
\caption[width=0.47\columnwidth]{}
\label{network_corridor}
\end{figure}
